Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex

We built a corpus of around 1 million lines of Fortran code from a
range of scientific computing packages: The Unified Model~\cite{um},
E3MG~\cite{RePEc:aen:journl:2006se-a12}, BLAS~\cite{blas},
Hybrid4~\cite{GBC:GBC635}, GEOS-Chem~\cite{geos-chem}, Navier (based
on \cite{griebel1997numerical}), Computational Physics
2~\cite{nicholas2006computational},
ARPACK-NG\footnote{\url{https://github.com/opencollab/arpack-ng}},
SPECFEM3D\footnote{\url{https://github.com/geodynamics/specfem3d}}.

>>>>

We built a corpus of around 1 million lines of Fortran code from a
range of scientific computing packages: The Unified Model~\cite{um},
E3MG~\cite{RePEc:aen:journl:2006se-a12}, BLAS~\cite{blas},
Hybrid4~\cite{GBC:GBC635}, GEOS-Chem~\cite{geos-chem}, Navier (based
on \cite{griebel1997numerical}), Computational Physics
2~\cite{nicholas2006computational},
ARPACK-NG~\cite{arpackng}, and
SPECFEM3D~\cite{specfem3d}.
